The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-12-28 r_r/submission/manuscript_rihe_r_r.Rmd
add revision submission files

---
title: "The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities"
#author: 
#  - Ozan Jaquette
#  - Crystal Han
#  - Irma Castañeda
bibliography: ./../other/burd_recruiting_chapter.bib
output:
  #bookdown::word_document2:
  bookdown::pdf_document2:
    toc: FALSE
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    keep_tex: true
csl: ./../other/apa.csl
urlcolor: blue
#always_allow_html: true
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \usepackage{setspace}
      - \usepackage{fancyhdr}
      - \usepackage{titlesec}
      #- \doublespacing
      - \floatsetup{capposition=top}
      - \newcommand{\beginsupplement}{
      - \setcounter{table}{0}  
      - \renewcommand{\thetable}{S\arabic{table}} 
      - \setcounter{figure}{0} 
      - \renewcommand{\thefigure}{S\arabic{figure}}}
fontsize: 12pt
---

@@

data_dir <- file.path('..', 'data')
tables_dir <- file.path('..', 'assets', 'tables')
figures_dir <- file.path('..', 'assets', 'figures')

>>>>

---
title: "The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities"
#author: 
#  - Ozan Jaquette
#  - Crystal Han
#  - Irma Castañeda
bibliography: ../../other/burd_recruiting_chapter.bib
output:
  #bookdown::word_document2:
  bookdown::pdf_document2:
    toc: FALSE
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    keep_tex: true
csl: ../../other/apa.csl
urlcolor: blue
#always_allow_html: true
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \usepackage{setspace}
      - \usepackage{fancyhdr}
      - \usepackage{titlesec}
      #- \doublespacing
      - \floatsetup{capposition=top}
      - \newcommand{\beginsupplement}{
      - \setcounter{table}{0}  
      - \renewcommand{\thetable}{S\arabic{table}} 
      - \setcounter{figure}{0} 
      - \renewcommand{\thefigure}{S\arabic{figure}}}
fontsize: 12pt
---

@@

data_dir <- file.path('..', '..', 'data')
tables_dir <- file.path('..', 'tables')
figures_dir <- file.path('.')

### 2023-12-28 r_r/submission/manuscript_rihe_r_r.tex
add revision submission files

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/nd_religion}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_count_pubu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_count_privu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_actual_proportional_pubu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_actual_proportional_privu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_u}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_region_pubu_privu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_religion_pubu_privu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_rank_pubu_privu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_race_pubu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_race_privu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_pubu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_privu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_2mode_u}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_count_pubu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_count_privu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_pubu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_privu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_enroll_pubu_privu}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_enroll_pubu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_comp_pubu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_comp_privu_privhs_pubhs}

>>>>

%!TEX TS-program = xelatex

@@

{\centering \includegraphics[width=2\linewidth]{./nd_religion}

@@

{\centering \includegraphics[width=2\linewidth]{./events_hs_count_pubu}

@@

{\centering \includegraphics[width=2\linewidth]{./events_hs_count_privu}

@@

{\centering \includegraphics[width=2\linewidth]{./events_hs_actual_proportional_pubu}

@@

{\centering \includegraphics[width=2\linewidth]{./events_hs_actual_proportional_privu}

@@

{\centering \includegraphics[width=2\linewidth]{./plot_1mode_u}

@@

{\centering \includegraphics[width=2\linewidth]{./ego_network_region_pubu_privu}

@@

{\centering \includegraphics[width=2\linewidth]{./ego_network_religion_pubu_privu}

@@

{\centering \includegraphics[width=2\linewidth]{./ego_network_rank_pubu_privu}

@@

{\centering \includegraphics[width=2\linewidth]{./ego_network_race_pubu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{./ego_network_race_privu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{./south_race_pubu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{./south_race_privu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{./plot_2mode_u}

@@

{\centering \includegraphics[width=2\linewidth]{./events_count_pubu}

@@

{\centering \includegraphics[width=2\linewidth]{./events_count_privu}

@@

{\centering \includegraphics[width=2\linewidth]{./plot_1mode_pubu}

@@

{\centering \includegraphics[width=2\linewidth]{./plot_1mode_privu}

@@

{\centering \includegraphics[width=2\linewidth]{./ego_network_enroll_pubu_privu}

@@

{\centering \includegraphics[width=2\linewidth]{./ego_network_enroll_pubu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{./south_race_comp_pubu_privhs_pubhs}

@@

{\centering \includegraphics[width=2\linewidth]{./south_race_comp_privu_privhs_pubhs}
